An Empirical Analysis of the Role of Energy in Economic Growth

### 2013-04-26 EconGrowth.Rnw
Additional edits to remove math formatting in section titles.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Historical Data}
\label{sec:Historical_Data}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%++++++++++++++++++++++++++++++
\subsection{Output ($Y$)} 
\label{sec:Output_Data}
%++++++++++++++++++++++++++++++

@@

%++++++++++++++++++++++++++++++
\subsection{Capital Stock ($K$)} 
\label{sec:Capital_Stock_Data}
%++++++++++++++++++++++++++++++

@@

%++++++++++++++++++++++++++++++
\subsection{Labor and Employment ($L$)} 
\label{sec:Labor_Data}
%++++++++++++++++++++++++++++++

@@

%++++++++++++++++++++++++++++++
\subsection{Thermal Energy, Exergy, and Useful Work ($E$)} 
\label{sec:Energy_Data}
%++++++++++++++++++++++++++++++

@@

%------------------------------
\subsubsection{Thermal Energy ($Q$)} 
\label{sec:Q_Data}
%------------------------------

@@

%------------------------------
\subsubsection{Exergy ($X$)} 
\label{sec:X_Data}
%------------------------------

@@

%------------------------------
\subsubsection{Useful Work ($U$)} 
\label{sec:U_Data}
%------------------------------

@@

Figure \ref{fig:Historical_Lattice_Graph} presents historical data, including indexed values for output ($y$), capital stock ($k$), labor ($l$), and the various energy quantifications ($q$, $x$, and $u$) for 1980-2011 (developed economies) and 1991-2011 (other economies). Factors of production track each other closely, and large covariances among these variables can be seen in Tables \ref{tab:Covariance_US} through \ref{tab:Covariance_ZM}.

@@

\section{Cobb-Douglas Models With Energy (CD$e$)}

@@

\subsection{Cobb-Douglas with thermal energy ($q$)}

@@

\subsection{Cobb-Douglas with exergy ($x$)}

@@

\subsection{Cobb-Douglas with useful work ($u$)}

@@

\subsection{CES with $Q$ (CES$q$)}

@@

\subsection{CES with $X$ (CES$x$)}

@@

\subsection{CES with $U$ (CES$u$)}

@@

\subsection{LINEX with $Q$}

@@

\subsection{LINEX with $X$}

@@

\subsection{LINEX with $U$}

@@

In the spirit of Reproducible Research \citep{Gandrud:2013vx}, all data, spreadsheets, \texttt{R} code \citep{R}, and other materials associated with this paper can be found at \url{https://github.com/MatthewHeun/Econ-Growth-R-Analysis}.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Sources of Data}
\label{sec:Sources_of_Data}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%++++++++++++++++++++++++++++++
\subsection{Economic Output} 
\label{sec:Economic_Output_Data}
%++++++++++++++++++++++++++++++

@@

%++++++++++++++++++++++++++++++
\subsection{Capital Stock} 
\label{sec:Capital_Stock_Data}
%++++++++++++++++++++++++++++++

@@

%++++++++++++++++++++++++++++++
\subsection{Labor and Employment}
\label{sec:Labor_Data}
%++++++++++++++++++++++++++++++

@@

%++++++++++++++++++++++++++++++
\subsection{Thermal Energy, Exergy, and Useful Work} 
\label{sec:Energy_Data}
%++++++++++++++++++++++++++++++

@@

%------------------------------
\subsubsection{Thermal Energy} 
\label{sec:Q_Data}
%------------------------------

@@

%------------------------------
\subsubsection{Exergy} 
\label{sec:X_Data}
%------------------------------

@@

%------------------------------
\subsubsection{Useful Work} 
\label{sec:U_Data}
%------------------------------

@@

Figure \ref{fig:Historical_Lattice_Graph} presents historical data, including indexed values for output ($y$), capital stock ($k$), labor ($l$), and the various energy quantifications ($q$, $x$, and $u$) for 1980-2011 (developed economies) and 1991-2011 (other economies). Factors of production track each other closely, and high covariances among these variables can be seen in Tables \ref{tab:Covariance_US} through \ref{tab:Covariance_ZM}.

@@

\section{Cobb-Douglas Models With Energy}

@@

\subsection{Cobb-Douglas with thermal energy}

@@

\subsection{Cobb-Douglas with exergy}

@@

\subsection{Cobb-Douglas with useful work}

@@

\subsection{CES with Thermal Energy}

@@

\subsection{CES with Exergy}

@@

\subsection{CES with Useful Work}

@@

\subsection{LINEX with Thermal Energy}

@@

\subsection{LINEX with Exergy}

@@

\subsection{LINEX with Useful Work}

@@

In the spirit of Reproducible Research \citep{Gandrud:2013vx}, all data, spreadsheets, \texttt{R} code \citep{R}, and other materials associated with this paper can be found at \protect\url{https://github.com/MatthewHeun/Econ-Growth-R-Analysis}.
